An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-31 EconGrowth2.Rnw
Added LINEX spaghetti graph to the paper.

Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.

<<LINEX_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
createLINEXLatticeGraph(energyType="Q")
@

>>>>

Figure~\ref{fig:LINEX_Spaghetti_Graph} compares LINEX model predictions to historical data.

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
cesSpaghettiGraph(data=spagDataLinex, facet_formula= ~ Country)
@
